Polytope notes

### 2020-03-22 notes/bo-FSD.tex
typo fixes in FSD

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
\usepackage{bbm}

@@

\vskip1em
\begin{theorem}
  Suppose $L: \reals^d \times \Y \to \nonnegreals$ is convex for each $y$ and indirectly elicits $\gamma$. Then for all $p \in \Delta_{\Y}$ and all $r \in \gamma(p)$,
    \[ d \geq \|p\|_0 - FSD(\gamma_r, p) - 1 . \]
\end{theorem}
\begin{proof}[IN PROGRESS]
  Let $u \in \argmin_{u'} L(u';p)$ and let $r = \psi(u)$.
  This implies $p \in \gamma_r$.

@@

  Now consider any $p'$ such that $\sum_y p'(y) w_y = \vec{0}$.
  This implies that $u$ is also an optimal report for $p'$, so $p' \in \gamma_r$ as well.
  Hence, if we write $W \in \reals^{d \times y$ as a matrix whose columns are $w_y$, we have
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : p' W = \vec{0} \}.  \]
  or maybe?
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : (p'-p) W = \vec{0} \}.  \]
  This is an equation in $|\Y|-1$ nonnegative variables with $d$ constraints, so the dimensionality of its solution is \bo{CHECK} at least $|\Y|-d-1$.

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{mathtools, amsthm, amsmath, amssymb, graphicx, verbatim}
\usepackage{xcolor}
\usepackage{bbm}

@@

\vskip1em
\begin{theorem}
  Suppose $L: \reals^d \times \Y \to \nonnegreals$ is convex for each $y$ and indirectly elicits $\gamma$. Then for all $p \in \Delta_{\Y}$ and all $r \in \gamma(p)$,
    \[ d \geq \|p\|_0 - FSD(\gamma_r, p) - 1 . \]
\end{theorem}
\begin{proof}[PROOF IN PROGRESS]
  Let $u \in \argmin_{u'} L(u';p)$ and let $r = \psi(u)$.
  This implies $p \in \gamma_r$.
  \bo{We don't get to choose $r$...}

@@

  Now consider any $p'$ such that $\sum_y p'(y) w_y = \vec{0}$.
  This implies that $u$ is also an optimal report for $p'$, so $p' \in \gamma_r$ as well.
  Hence, if we write $W \in \reals^{d \times |\Y|}$ as a matrix whose columns are $w_y$, we have
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : p' W = \vec{0} \}.  \]
  or maybe?
    \[ \gamma_r \supseteq \{p' \in \Delta_{\Y} : (p'-p) W = \vec{0} \}.  \]
  This is an equation in $|\Y|-1$ nonnegative variables with $d$ constraints, so the dimensionality of its solution is \bo{CHECK} at least $|\Y|-d-1$.
